\begin{center}
	{\large \textbf{Acknowledgments}}\\
\end{center}

\paragraph{}I would like to thank everybody that played a role in completing this step of my life. I know there is no way that I could go one by one through every person that helped and thank them. I am sure that it would take too many pages and then I would leave somebody out. There are a few special people, that I would like to call out. 
\paragraph{}First, I would like to thank my brother, James for the courage to change career paths and my parents, Barb, Howard, and Deb for the support and guidance. Thanks to Dallas and Jennifer, for housing me for a few months. Thank you Dr. Fomin for targeting my weakness, the beach, and giving me the chance to join the JLab community. Also, I would like to thank Dr. Fomin for supporting my research and guiding me though the swamps of PhD. research. I would like to thank the JLab community specially Dr. Higinbotham for accepting me into the community and helping through this journey including keeping the office door open for me to drop in a million times! I would also like to thank my committee for guiding me through my defense and allowing me to graduate. 
\paragraph{}I would really like to thank the extended tritium family of grad students and post docs. Working with such a great group of people from around the world has truly been amazing!! Thank you, Sheren, Scott, Jessica, Tyler H., Hanjie, Dien, Mike, Tong, Shujie, Rey, Johnathan, Tyler K., Nathaly, Bishnu, Evan, Florian, Luke, Marco, and Zhihong. Lastly and I think the person deserving of the most thanks, is my wife, Callie. Thank you so much for everything! Specially thank you for dropping everything and coming on this adventure with me!.

\paragraph{}I would like to thank the DOE and JSA for financial support throughout my time at JLab. 